The Hydrogen Epoch of Reionization Array Dish: Characterization with Electromagnetic Simulations

### 2016-01-26 DishSimulations/paper/DishSimulationsPaper_v2.tex
latest simulations paper update

\documentclass[twocolumn]{emulateapj}
\usepackage{amsmath}
\usepackage{graphicx}
\usepackage{natbib}
\citestyle{aa}

@@

\altaffiltext{1}{MIT Kavli Institute for Cosmological Physics}
\altaffiltext{2}{MIT Dept. of Physics}
\altaffiltext{3}{National Radio Astronomy Obs., Charlottesville VA}
\altaffiltext{4}{Dept. of Astronomy, U. Virginia, Charlottesville VA}
\altaffiltext{5}{Astronomy Dept. U. California, Berkeley CA}
\altaffiltext{6}{School of Earth and Space Exploration, Arizona State U.,
\altaffiltext{7}{Stellenbosh}
Tempe AZ}
\begin{abstract}
Using electromagnetic simulations, we assess the spectral properties of the antenna element of the Hydrogen Epoch of Reionization Array (HERA) in order to both establish a specification for the degree of spectral structure that is permissible to sufficiently isolate foregrounds and allow a detection of the cosmological 21\,cm signal and verify direct laboratory measurements of the dish characteristics. We find that our simulations are in good agreement with field measurements. Using simulations of foregrounds, we find that the $\approx -40$\,dB response at 60\,ns of the HERA dish is sufficient to isolate the cosmological 21\,cm signal $\approx 0.2$\,$h$Mpc$^{-1}$ at $z\approx 8.5$ and obtain a high signal to noise detection of the power spectrum. This study represents the first time that direct measurements a 21\,cm interferometer design have been translated into its ability to constrain the physics of reionization. 
\end{abstract}
\section{Introduction}
Observations of the redshift 21\,cm radiation neutral hydrogen in the intergalactic medium (IGM) have the potential to illuminate the hitherto unobserved {\it dark ages} and {\it cosmic dawn}, revolutionizing our understanding of the first UV and X-ray sources in the universe and how their properties influenced galactic evolution (see \citet{Furlanetto:2006Review}, \citet{Morales:2010}, and \citet{Pritchard:2012} for reviews). As of now, two major experimental endeavors are underway to make a first detection of the 21\,cm signal with most focusing on the Epoch of Reionization (EoR) in which UV photons from early galaxies transformed the hydrogen in the universe from neutral to ionized. The first involves measuring the sky-averaged global signal and is being pursued by experiments such as EDGES \citep{Bowman:2010}, LEDA \citep{Greenhill:2012}, DARE \citep{Burns:2012}, SciHi \citep{Voytek:2014}, and BIGHORNS \citep{Sokolowski:2015} coming online in their planning stages or taking data. The second attempts to observe spatial  fluctuations in the 21\,cm emission using radio interferometers. As of now, a first generation of interferometry experiments are taking data in an attempt to make a first statistical detection of the power spectrum of 21\,cm brightness temperature fluctuations. These include the Giant Metrewave Telescope (GMRT)  \citep{Paciga:2013}, the Low Frequency ARray (LOFAR), \citep{VanHaarlem:2013}, the Murchison Widefield Array \citep{Tingay:2013} and the Precision Array for Probing the Epoch of Reionization (PAPER) \citep{Parsons:2010}.

The primary obstacle to obtaining a high redshift detection of the cosmological signal through both of these methods is the existence of foregrounds that are $\sim 10^5-10^6$ times brighter. While requiring much greater sensitivity to global-signal experiments, interferometers have the advantage that these spectrally smooth foregrounds naturally avoid a significant region of $k$-space, known as the {\it EoR window}, occupying a region known as the {\it wedge} \citep{Datta:2010,Vedantham:2012,Parsons:2012,Thyagarajan:2013,Liu:2014a,Liu:2014b}, however any structure in the frequency response of the instrument has the potential to leak foregrounds into the EoR window, masking our signal. Indeed, low level spectral structures in the analogue and digital signal chains on the initial buildout of the MWA are proving to be a significant obstacle \citep{Dillon:2015b,EwallWice:2015a,Beardsley:2015b}.

While, in principle, spectral structure in the bandpass of the instrument may be removed in calibration, simulations show that any mismodeling of emission and the primary beam, potentially below the confusion limit, will mix the significant spectral structure on long baselines into short ones, masking the signal entirely \citep{Barry:2015}. While redundant calibration \citep{Wieringa:1992,Liu:2011,Zheng:2014} is able to calibrate the independent of a detailed model of the sky, any direction-dependent chromatic structure in the primary beam of the instrument introduces additional degrees of freedom that must be modeled, potentially leading to signal loss and the introduction of spurious spectral structure due to unmodeled foregrounds in long baselines. Because of our limited knowledge of foregrounds at low-frequency and the fidelity of calibration algorithms, the only sure way of building an instrument that will guarantee a detection of the redshifted 21\,cm emission is to design it such that all spectral structure in the signal chain is limited to a finite region of delay space, well below the wedge.

The Hydrogen Epoch of Reionization Array (HERA) is an instrument currently taking first observations in the Karoo in South Africa with the ultimate goal of detecting the power spectrum of 21\,cm brightness temperature fluctuations at high signal-to-noise (SNR) \citep{Pober:2014}. A central principle in HERA's design is that it be calibration fail-safe such that a detection of the signal is guaranteed, even if the chromaticity of the instrument is not calibrated out. This paper and its companions \citep{Neben:2015b,Patra:2015,Thyagarajan:2015c} describe a multifaceted approach to establishing a stringent specification on the spectral structure permissible for HERA to be calibration fail-safe and determine to what extent its design meets these requirements. We accomplish this by establishing a spec with simulations of foregrounds \citep{Thyagarjan:2015c} and verifying that HERA primary antenna element meets this spec with reflectometry \citep{Patra:2015} and Orbcomm beam mapping \citep{Neben:2015b}. These measurements are verified with detailed electromagnetic simulations which we describe in this work.

This paper is organized as follows. In \S~\ref{sec:Formalism} we lay out our analytic framework for describing the impact of reflections and spectral structure on foreground leakage in delay-transform power spectra. In \S~\ref{sec:Simulations} we describe our electromagnetic simulations of the HERA dish element. In \S~\ref{sec:Comparison} we compare our simulation results to direct measurements of the primary dish element and in \S~\ref{sec:Foregrounds} we apply our electromagnetic simulation results to simulations of foregrounds to determine the extent that the HERA dish's chromatic structure pollutes the EoR window and their impact on HERA's overall sensitivity. We conclude in \S~\ref{sec:Conclusion}.

\section{The Impact of Reflections on Delay-Transform Power Spectra}\label{sec:Formalism}
In this section, we show how reflections in the analogue signal path of an antenna lead to foreground contamination of the EoR window. Intuitively, any reflections in the signal path introduce sinusoidal ripples in the frequency dependent gain of the instrument. Since reflection delay is the Fourier dual to frequency, reflections at larger delays introduce ripples at higher frequencies. Isolation of the 21\,cm signal from foregrounds that are over five orders of magnitude brighter depends critically on their smoothness. Any sinusoidal frequency structure, introduced by the antenna gain will cause these foregrounds to mimic and swamp the signal unless they are brought below a level similar to the ratio between the foregrounds and the signal itself. We now derive this process in formal detail. A simple equation for effect of direction independent reflections in the signal chain of an interferometer, downstream of the receiver, has been derived in \citet{EwallWice:2015a}, we extend this analysis in this section by considering the direction dependent reflections that can occur within the antenna element. We assume that the intensity field on the sky is given by 
\begin{equation}\label{eq:Dirac}
I({\bf \widehat{k}},f) \delta_D({\bf \hat{k}} - {\bf \hat{k}'})= \langle s({\bf \hat{k}},f)s^*({\bf \hat{k}'},f)  \rangle_t^2
\end{equation}
 where $\delta_D$ is the Dirac delta function and $\langle \rangle_t$ indicates an average in time. We imagine that the electric field as a function of time, $\widetilde{s}({\bf \widehat{k}},t)$ arrives at an arbitrary origin at time $t$ and at the various $i^{th}$ antenna elements of an interferometer at locations ${\bf x_i}$ at times $\tau_i={\bf x_i} \cdot {\bf \widehat{k}} /c$. We now consider reflections within a single dish element described by a direction dependent reflection coefficient\footnote{Ignoring reflections between multiple dish elements which we treat in Appendix~\ref{app:Reflections}}, $\widetilde{r}_i({\bf \widehat{k}},\tau)$. which re-introduce the signal at later times $\tau$. The voltage signal measured at the $i^{th}$ antenna element, $\widetilde{v}_i$, is the integral over solid angle of the convolution of the electric field entering the antenna (delayed by $\tau_i$) with $r_i({\bf \widehat{k}},\tau')$.

\begin{equation}
\widetilde{v}_i(t) = \int d \Omega \int d \tau \widetilde{r}_i({\bf \widehat{k}},\tau) \widetilde{s}({\bf \widehat{k}},t- \tau_i - \tau)
\end{equation}

A correlator (FX and XF) measures the time-averaged product of the Fourier transform of the voltage streams between the $i^{th}$ and $j^{th}$ antenna. Fourier transforming the voltage stream from the $i^{th}$ antenna we obtain
\begin{equation}
v_i(f) = \int d \Omega \int d \tau \widetilde{r}_i({\bf \widehat{k}},\tau) s({\bf \widehat{k}},f)e^{-2 \pi i f(\tau_i+\tau)}
\end{equation}
The time averaged product between the two antennas is
\begin{equation}
V_{ij}'(f) = \left \langle v_i(f) v_j^*(f) \right \rangle_t = \int d \Omega \int d \tau \widetilde{r}_i(\tau) d \tau' \widetilde{r}^*_j(\tau')e^{-2 \pi i f (\tau-\tau') } I({\bf \widehat{k}}, f) e^{- 2 \pi i \Delta \tau_{ij}f} 
\end{equation}
where $\Delta \tau_{ij} = \tau_i-\tau_j = ({\bf x_i - x_j}) \cdot {\bf \widehat{k}}/c$. We eliminated one of the solid angle integrals using equation~\ref{eq:Dirac}.

Defining ${\bf u}_{ij} = f ({\bf x}_i-{\bf x}_j)/c$, we obtain,
 %HERA's primary antenna element consists of a sleeved dipole element suspended 5\,m above the focus of a 14\,m diameter parabolic dish (Fig.~\ref{fig:Dish}).
.
%\begin{figure}
%\includegraphics[width=.5\textwidth]{figures/DishSA.png}
%\caption{The HERA primary antenna element-one of 19 undergoing currently taking the first observations in the Karoo in South Africa. The antenna consists of a sleeved dipole suspended within a 2\,m diameter skirt, five meters above the ground at the focal point of a 14\,m diameter dish.}\label{fig:Dish}
%\end{figure}

% We show in Appendix~\ref{app:Reflections} that if an astronomical radio signal with time dependence at the location of the feed, $s({\bf \widehat{k}},t)$, experience reflections within the dish such that the voltage recorded in the feed is

Than the resulting visibilities obtained by cross correlating antenna $i$ and antenna $j$ are given by 
\begin{equation}\label{eq:Visibility}
V'_{ij}(f) =  \int d \Omega r_i({\bf \widehat{k}},f) r^*_j({\bf \widehat{k}},f)  I(f,{\bf \widehat{s}})e^{2 \pi i f {\bf u}_{ij} \cdot {\bf \widehat{k}}/c},
\end{equation}
where ${\bf b}_{ij} = ({\bf x}_i - {\bf x}_j )$ to use the usual $uv$ notation of interferometry. $r_i({\bf \hat{k}},f)$ is the inverse fourier transform of the reflection response of the dish, hence we see that the reflection response is precisely the Fourier dual to the Dish's frequency domain voltage beam. Setting a specification on reflections is hence equivalent to setting a specification on the spectral smoothness of the voltage beam.

In order to separate spectrally smooth foregrounds from our signal, we expect to use the {\it delay transform} over frequency, defined as \citep{Parsons:2012}

@@

\widetilde{V}_{ij}(\tau) = \int d f e^{2 \pi i \tau f} V_{ij}(f)

@@

\widetilde{V}'_{ij}(\tau)=  \int d \Omega \int d f  r_i({\bf \widehat{k}},f) r_j^*({\bf \widehat{k}},f)  I(f,{\bf \hat{k}}) e^{2 \pi i f ( {\bf b}_{ij} \cdot {\bf \hat{k}} /c - \tau)}

@@

Let's examine the quantity within the angular integral. For each ${\bf \hat{k}}$, we see that each source is mapped to a line $\tau ={\bf b}_{ij}\cdot{\bf \hat{k}}/c$, resulting in the much discussed ``wedge" \citep{Datta:2010,Vedantham:2012,Parsons:2012,Morales:2013,Thyagarajan:2013,Liu:2014a,Liu:2014b}. The presence of the frequency dependent beam causes each source line to be convolved in delay with the direction dependent kernel

@@

\widetilde{R}_{ij}({\bf \hat{k}},\tau) = \int d \tau \widetilde{r}_i({\bf \widehat{k}},\tau - \Delta \tau) \widetilde{r}^*_j({\bf \widehat{k}},-\Delta \tau).

@@

which is the convolution of the delay response of voltage beam $i$ with the complex conjugate of voltage beam $j$ evaluated on a negative t-axis, $\widetilde{r}_i({\bf \widehat{k}},\tau)$,$\widetilde{r}_j({\bf \widehat{k}},\tau)$. Note that this is not equal to the convolution of the voltage response with its complex conjugate, which would lead to foreground power only being bled out to positive delays. Usually, beams have a different delay structure in each direction, and we demonstrate the effect of foreground smearing in Fig.~\ref{fig:Smearing} for a simple model with only three sources. Without reflections, the sources would form lines in $b-\tau$ space. With the reflections, the sources are smeared out, leading to supra-horizon emission. 
\begin{figure*}[h!]

@@

\caption{We demonstrate the impact on foregrounds of the frequency dependent beam. Left: The location of three sources in delay space assuming a frequency indepdendent beam (no reflections in the antenna element). Right: the presence of chromaticity due to reflections in the antenna smears the source in delay with the kernel given by equation~\ref{eq:Kernel}. Since the frequency response of the dish are a function of direction on the sky, the shape of the delay kernel is different for each source line. We see that this smearing can lead to substantial supra-horizon emission. Sources near zenith (low delay) tend to have a larger maximum since the beam gain is larger near zenith, but a more compact kernel (since beam bore-sights tend to have less spectral structure). Meanwhile, sources near the horizon have a much smaller maxima but have less compact kernels.}

@@

For the sake of pedagogy, we now consider the case where the beam can be factored into angular and frequency dependent components, $r_i({\bf \hat{k}},f) = g_i(f)a_i({\bf \hat{k}})$. For such a case, every line in Fig.~\ref{fig:Smearing} would be convolved with the same delay dependent shape, normalized to the gain of $a_i({\bf \hat{k}})$. In this case, we have

@@

We can further simplify matters by assuming that $\widetilde{g}_i(\tau=0)\gg\widetilde{g}_i(\tau>0)$, which is often a good assumption at large delays for the relatively smooth bandpasses our instruments are designed to have. 
\begin{equation}\label{eq:KernelApprox}
\widetilde{V}_{ij}'(\tau) \approx \widetilde{g}_i(0)\int d \tau' \widetilde{g}_j^*(\tau')\widetilde{V}_{ij}(\tau- \tau') + \widetilde{g}_j^*(0) \int d \tau' \widetilde{g}_i(\tau')\widetilde{V}_{ij}(\tau-\tau') 
Hence, to first order, the impact of reflections is to convolve the delay-transformed visibility with the voltage beam of the instrument, which acts as the power-kernel. This may be a somewhat un-intuitive result since we might naively expect for the power-kernel to be the square of the delay-response. This linear falloff puts exquisite requirements on the smoothness of the beam, requiring that it fall roughly six orders of magnitude in delay before the signal is accessible.

 In this paper, we derive $\widetilde{r}_i({\bf \widehat{k}},\Delta \tau)$ for the HERA antenna element using electromagnetic simulations, in order to verify direct measurements of the antenna element with refelctometry \citep{Patra:2015} and Orbcomm measurements of the beam \citep{Neben:2015b}. We also explore the implications of the HERA dish's $\widetilde{r}_i({\bf \widehat{k}},\tau)$ on the scientific bottom line for EoR, using the Fisher Matrix Formalism.

\section{Electromagnetic Simulations of the HERA dish element}\label{sec:Simulations}
In Fig.~\ref{fig:SimulationSetup} we show the geometery of the electromagnetic simulation. {\bf Rich: fill in the details here}
\begin{figure}

\subsection{The Simulations}
\includegraphics[width=.5\textwidth]{figures/One_dish_Pfeed_render_pw_0deg.png}
\caption{A rendering of our time domain simulation at $t=0$, demonstrating the geometry and setup of our electromagnetic simulation. The plane wave is started just above the feed (red plane).}\label{fig:SimulationSetup}
\end{figure}

>>>>

\newcommand{\bx}{{\bf x}}
\newcommand{\bl}{\boldsymbol{\ell}}
\newcommand{\fts}{{\widetilde{s}}}
\newcommand{\ftr}{{\widetilde{r}}}
\newcommand{\ftv}{{\widetilde{v}}}
\newcommand{\bu}{{\bf u}}
\newcommand{\bb}{{\bf b}}
\newcommand{\ftR}{{\widetilde{R}}}

\documentclass[twocolumn]{emulateapj}
\usepackage{amsmath}
\usepackage{graphicx}
\usepackage{natbib}
\usepackage{color}
\citestyle{aa}

@@

\altaffiltext{1}{MIT Kavli Institute for Cosmological Physics}
\altaffiltext{2}{MIT Dept. of Physics}
\altaffiltext{3}{National Radio Astronomy Obs., Charlottesville VA}
\altaffiltext{4}{Dept. of Astronomy, U. Virginia, Charlottesville VA}
\altaffiltext{5}{Astronomy Dept. U. California, Berkeley CA}
\altaffiltext{6}{School of Earth and Space Exploration, Arizona State U.,
\altaffiltext{7}{Stellenbosh}
Tempe AZ}
\begin{abstract}
We use time domain electromagnetic simulations to assess the spectral characteristics of the antenna element for the Hydrogen Epoch of Reionization Array (HERA). These simulations are part of a multi-faceted campaign to determine whether the dish's design is suitable for obtaining a detection of redshifted 21\,cm emission from the Epoch of Reionization. Our simulations show the existence of standing wave reflections in some regions of the 100-200\,MHz bandpass with an amplitude of $\approx -35$\,dB at 100\,ns which can lead to some loss of measurable modes and a modest reduction in sensitivity over a small segment of the band. Overall, we find that the spectral response of the dish is sufficiently smooth for proven foreground isolation methods such as delay filtering to contain foreground emission at line of sight wave numbers below $k_\parallel = 0.15-0.2$\,$h$Mpc$^{-1}$. Incorporating these results into a Fisher Matrix analysis, we find that the spectral structure observed in our simulations has only a small effect on the overall constraints on the astrophysics of reionization that HERA will achieve, allowing it to serve as a benchmark for the design of future instruments such as the Square Kilometer Array. 
\end{abstract}
\section{Introduction}
Observations of the redshift 21\,cm radiation neutral hydrogen in the intergalactic medium (IGM) have the potential to illuminate the hitherto unobserved {\it dark ages} and {\it cosmic dawn}, revolutionizing our understanding of the first UV and X-ray sources in the universe and how their properties influenced galactic evolution (see \citet{Furlanetto:2006Review}, \citet{Morales:2010}, and \citet{Pritchard:2012} for reviews). As of now, two major experimental endeavors are underway to make a first detection of the 21\,cm signal with most focusing on the Epoch of Reionization (EoR) in which UV photons from early galaxies transformed the hydrogen in the universe from neutral to ionized. The first involves measuring the sky-averaged global signal and is being pursued by experiments such as EDGES \citep{Bowman:2010}, LEDA \citep{Greenhill:2012,Bernardi:2015}, DARE \citep{Burns:2012}, SciHi \citep{Voytek:2014}, and BIGHORNS \citep{Sokolowski:2015} either in their planning stages or already taking data. The second attempts to observe spatial  fluctuations in the 21\,cm emission using radio interferometers. A first generation of such experiments are currently taking data in an attempt to make a first statistical detection of the power spectrum of 21\,cm brightness temperature fluctuations. These include the Giant Metrewave Telescope (GMRT)  \citep{Paciga:2013}, the Low Frequency ARray (LOFAR), \citep{VanHaarlem:2013}, the Murchison Widefield Array \citep{Tingay:2013a} and the Precision Array for Probing the Epoch of Reionization (PAPER) \citep{Parsons:2010}. Already, these experiments are beginning to yield upper limits on the 21\,cm signal \citep{Dillon:2013,Parsons:2014,Jacobs:2015,Dillon:2015,EwallWice:2015a} and significant scientific results. The most stringent measurement of $\approx 500$\,mK$^2$ \citep{Ali:2015} is able to rule out number of scenarios in which the intergalactic medium received little or no heating from X-rays \citep{Pober:2015,Greig:2015b}.

The primary obstacle to obtaining a high redshift detection of the cosmological signal through both of these methods is the existence of foregrounds that are $\sim 10^5-10^6$ times brighter. While requiring much greater sensitivity than global-signal experiments, interferometers have the advantage that spectrally smooth foregrounds are naturally contained to a finite region of Fourier space, corresponding to large line of sight scales, known as the {\it wedge} \citep{Datta:2010,Vedantham:2012,Parsons:2012,Thyagarajan:2013,Liu:2014a,Liu:2014}. However any structure in the frequency response of the instrument is imprinted on the foregrounds and has the potential to leak power into the {\it EoR window} at small line of sight scales, masking the signal. Indeed, sub-percent spectral features in the analogue and digital signal chains on the initial build-out of the MWA are proving to be a significant obstacle \citep{Dillon:2015b,EwallWice:2015a,Beardsley:2015b}.

While, in principle, spectral structure in the bandpass of the instrument may be removed in calibration, simulations show that any mismodeling of emission and the primary beam, potentially below the confusion limit, will mix the significant spectral structure introduced by the wedge on long baselines into short ones, masking the signal entirely \citep{Barry:2016}. While redundant calibration \citep{Wieringa:1992,Liu:2011,Zheng:2014} is able to solve for gains that are primarily independent of a detailed model of the sky, it is unclear how one might remove direction-dependent chromatic structure that might be present in the primary beam of the instrument. Because of our limited knowledge of foregrounds at low frequency and the fidelity of calibration algorithms, it is imperitive to design experiments whose spectral structure is contained, as much as possible, to low delays.

The Hydrogen Epoch of Reionization Array (HERA) is a next generation 21\,cm experiment designed to achieve a two-orders of magnitude improvement in sensitivity over current experiments which will allow it to make a robust detection of the 21\,cm power spectrum during the EoR \citep{Pober:2014}. Much of this sensitivity increase is enabled by moving the collecting area of the instrument into baselines that are located primarily inside of the EoR window and a switch from PAPER's skirted dipoles and the MWA's phased dipole arrays to an antenna element that consists of a feed suspended over a large reflecting parabolic dish. A central requirement for HERA's dish design is that the antenna have a response that is sufficiently smooth in frequency and centralized enough in its angular response that it leaves the EoR window free of contamination since one cannot rely on direction independent redundant calibration to remove any spectral structure that varies as a function of location on the primary beam.

This paper and its companions \citep{Neben:2016,Patra:2016,Thyagarajan:2016} describe a multifaceted approach for assessing whether the HERA dish meets the requirements for isolating foregrounds within the wedge and leaving the EoR window clean. We accomplish this by establishing a spec with simulations of foregrounds \citep{Thyagarajan:2016} and verifying that HERA primary antenna element meets this spec with reflectometry \citep{Patra:2016} and Orbcomm beam mapping \citep{Neben:2016}. In this work, we present the results of time-domain electromagnetic simulations that are intended to predict the degree of spectral structure in the HERA dish, assess the impact of this spectral structure on the leakage of foregrounds into the EoR window, and to verify the reflectometry measurements taken in the field by \cite{Patra:2016}.

This paper is organized as follows. In \S~\ref{sec:Formalism} we lay out our analytic framework and describe the impact of reflections and spectral structure on foreground leakage in delay-transform power spectra. In \S~\ref{sec:Simulations} we describe our time-domain electromagnetic simulations of the HERA dish element and how we extract the voltage response function. In \S~\ref{sec:SimulationResults} we describe the results and verify our simulation framework by comparing its prediction of the $S_{11}$ parameter of the HERA dish to direct field measurements described in \citep{Patra:2016}. In \S~\ref{sec:Foregrounds} we apply our electromagnetic simulation results to simulations of foregrounds to determine the extent that the HERA dish's chromatic structure pollutes the EoR window and their impact on HERA's overall sensitivity. We conclude in \S~\ref{sec:Conclusion}.

\section{The Impact of Reflections on Delay-Transform Power Spectra}\label{sec:Formalism}
In this section, we show how reflections in the analogue signal path of an antenna lead to foreground contamination of the EoR window. Intuitively, any reflections in the signal path introduce sinusoidal ripples in the frequency dependent gain of the instrument. Since time delay is the Fourier dual to frequency, reflections with larger delays introduce ripples at higher frequencies. Isolation of the 21\,cm signal from foregrounds that are over five orders of magnitude brighter depends critically on their smoothness. Any sinusoidal frequency structure introduced by the reflections will cause these foregrounds to mimic and swamp the signal unless they are brought below a level similar to the ratio between the foregrounds and the signal itself. A simple equation describing effect of direction independent reflections in the signal chain of an interferometer, downstream of the receiver on a visibility has been derived in \citet{EwallWice:2015a}. We now extend this analysis by considering the direction dependent reflections that can occur within the antenna element. 
We start by denoting the electric field of radiation arriving at an $i^{th}$ antenna element at position $\bx_i$ and time $t_i = t + \bl \cdot \bx_i /c \equiv t+\tau_i$ as $\fts(\bl,\bx_i,t_i)$.

Reflections within the signal chain of each antenna are most generally described by a direction dependent reflection coefficient, $\ftr_i(\bl,\tau)$. Its effect is to add the signal to itself multiplied by $\ftr_i$ and delayed by $\tau$. The voltage signal measured at the $i^{th}$ antenna element, $\widetilde{v}_i$, is the integral over solid angle of the electric fields arriving from all directions. The presence of the reflections introduces a convolution of the electric field entering the antenna (delayed by $\tau_i$) with $\ftr_i(\bl,\tau)$.

\begin{equation}\label{eq:Voltage}
\ftv_i(t) = \int d \Omega \int d \tau \ftr_i(\bl,\tau) \fts(\bl,t+ \tau_i - \tau)
\end{equation}

A correlator measures the time-averaged product of the Fourier transform of the voltage streams between the $i^{th}$ and $j^{th}$ antenna. Fourier transforming the voltage stream from the $i^{th}$ antenna we obtain
\begin{equation}
v_i(f) = \int d \Omega \int d \tau \ftr_i(\bl,\tau) s(\bl,f)e^{-2 \pi i f(\tau_i+\tau)}
\end{equation}
The time averaged product between the two antennas is
\begin{align}
V_{ij}'(f) &= \left \langle v_i(f) v_j^*(f) \right \rangle_t \nonumber \\
 &= \int d \Omega d \tau d \tau' \ftr_i(\tau) \ftr^*_j(\tau')e^{-2 \pi i f (\tau-\tau') } I(\bl, f) e^{- 2 \pi i \Delta \tau_{ij}f} 
\end{align}
where $\Delta \tau_{ij} = \tau_i-\tau_j = (\bx_i-\bx_j) \cdot \bl/c$ and $I(\bl,f)=\left \langle |s(f,\bl)|^2 \right \rangle_t$. Here, we have invoked the fact that electromagnetic waves arriving from different directions are incoherent.

Defining $\bu_{ij} = f (\bx_i-\bx_j)/c$ and performing the $\tau$ and $\tau'$ Fourier transforms, we arrive at
\begin{equation}\label{eq:Visibility}
V'_{ij}(f) =  \int d \Omega r_i(\bl,f) r^*_j(\bl,f)  I(\bl,f)e^{2 \pi i f \bu_{ij} \cdot \bl/c},
\end{equation}
where ${\bf b}_{ij} = ({\bf x}_i - {\bf x}_j )$ to use the usual $uv$ notation of interferometry. $r_i(\bl,f)$ is the inverse fourier transform of the reflection response of the dish, hence we see that the reflection response is precisely the Fourier dual to the Dish's frequency domain voltage beam. Setting a specification on reflections is hence equivalent to setting a specification on the spectral smoothness of the antenna's voltage beam.

In order to filter spectrally smooth foregrounds from the signal,HERA is expected to employ the {\it delay transform} over frequency, defined as \citep{Parsons:2012}

@@

\widetilde{V}_{ij}(\tau) = \int d f e^{2 \pi i \tau f} V_{ij}(f).

@@

\widetilde{V}'_{ij}(\tau)=  \int d \Omega \int d f  r_i(\bl,f) r_j^*(\bl,f)  I(\bl,f) e^{2 \pi i f ( \bb_{ij} \cdot \bl /c - \tau)}

@@

Let's examine the quantity within the angular integral. We see that each source located at $\bl$ on the sky is mapped to a line $\tau =\bb_{ij}\cdot \bl/c$, resulting in the much discussed ``wedge" \citep{Datta:2010,Vedantham:2012,Parsons:2012,Morales:2012,Thyagarajan:2013,Liu:2014a,Liu:2014b}. The presence of the frequency dependent beam causes each source line to be convolved in delay with the direction dependent kernel

@@

\ftR_{ij}(\bl,\tau) = \int d \tau \ftr_i(\bl,\tau - \Delta \tau) \ftr^*_j(\bl,-\Delta \tau).

@@

which is the convolution of the delay response of the voltage beam of antenna $i$ with the time-reversed complex conjugate of voltage beam of antenna $j$. In the remainder of this paper, we will often refer to $\ftR$ as the {\it power kernel} applied to a visibility. Note that this is not equal to the convolution of the voltage response with its complex conjugate, which would lead to foreground power only being bled out to positive delays. We demonstrate the effect of foreground smearing in Fig.~\ref{fig:Smearing} for a simple model with only three sources. Without reflections, the sources would form lines in $b-\tau$ space. Withthe reflections, the sources are smeared out, leading to supra-horizon emission. 
\begin{figure*}

@@

\caption{A demonstration of the impact on foregrounds of the frequency dependent beam. Left: The location of three sources in delay space assuming a frequency indepdendent beam (no reflections in the antenna element). Right: the presence of chromaticity due to reflections in the antenna smears the source in delay with the kernel given by equation~\ref{eq:Kernel}. Since the frequency response of the dish are a function of direction on the sky, the shape of the delay kernel is different for each source line. We see that this smearing can lead to substantial supra-horizon emission. Sources near zenith (low delay) tend to have a larger maximum since the beam gain is larger near zenith, but a more compact kernel (since beam bore-sights tend to have less spectral structure). Meanwhile, sources near the horizon have a much smaller maxima but have less compact kernels.}

@@

For the sake of pedagogy, we now consider the case where the beam can be factored into angular and frequency independent components, $r_i(\bl,f) = g_i(f)a_i(\bl)$. For such a case, every line in Fig.~\ref{fig:Smearing} would be convolved with the same delay dependent shape, normalized to the gain of $a_i(\bl)$. In this situation, we have

@@

where $V_{ij}$ is the visibility with the achromatic factor in the voltage patterns included. 
We can gain further insight into the behavior of the delay kernel arising from chromaticity by assuming that $\widetilde{g}_i(\tau=0)\gg\widetilde{g}_i(\tau>0)$, which should be the case at large delays for the smooth bandpasses our instruments are designed to have. 
\begin{align}\label{eq:KernelApprox}
\widetilde{V}_{ij}'(\tau) &\approx \widetilde{g}_i(0)\int d \tau' \widetilde{g}_j^*(\tau')\widetilde{V}_{ij}(\tau- \tau') \nonumber \\
& + \widetilde{g}_j^*(0) \int d \tau' \widetilde{g}_i(\tau')\widetilde{V}_{ij}(\tau-\tau') 
Hence, to first order, the impact of reflections is to convolve the delay-transformed visibility with the voltage beam of the instrument. This may be a somewhat un-intuitive result since naive dimensional analysis might predict that the power-kernel to be proportional to the square of the delay-response. This linear falloff coupled with the enormous dynamic range between foregrounds and signal puts exquisite requirements on the smoothness of the beam, requiring that it fall roughly six orders of magnitude in the regions of delay space that we want to measure the signal.

\section{Electromagnetic Simulations of the HERA dish element}\label{sec:Simulations}

HERA \citep{DeBoer:2016} is an instrument designed to detect the power spectrum of 21\,cm brightness temperature fluctuations during the EoR at high signal-to-noise between the frequencies of 100 and 200\,MHz (redshifts 6 to 12) \citep{Pober:2014}. Its initial, 19-element, buildout is currently taking first observations in the Karoo in South Africa. HERA is meant to serve as a vast improvement in sensitivity over current efforts for only a modest increase in cost. It achieves this by increasing the number of correlated inputs by only a factor of $\approx 2$ while increasing the total collecting area of each correlated element by over an order of magnitude and arranging the elements in such a way as to maximize the number of short baselines that are located outside of the foreground wedge. Central to increasing the collecting area of each element is a switch from dipoles (used by the MWA and PAPER) to feeds suspended over large 14\,m diameter parabolic dishes. In Fig.~\ref{fig:AntennaComparison} we show one of the initial 19 dishes currently being deployed in South Africa at the same site as PAPER whose antenna we also show at the top of the figure.

Having formally derived the impact of analogue reflections on foreground visibilities, we are now in a position to investigate their existence in the HERA dish. In this section, we describe the setup and parameters of our simulations (\S~\ref{ssec:Simulations}), and how we extract the voltage response function of the dish (\S~\ref{ssec:Deconvolve}).

\begin{figure}
\includegraphics[width=.5\textwidth]{figures/PAPER_HERA_compare.jpg}
\caption{The HERA antenna element (bottom) uses a parabolic dish to achieves over an order of magnitude increase in collecting area over the PAPER antenna (top). The sleeved dipole in the center of the PAPER backplane is identical to the sleeved dipole being suspended under the cylindrical skirt over the vertex of the HERA dish. The dish geometry has the potential to introduce intra-antenna reflections which we explore in this work.}
\label{fig:AntennaCompare}
\end{figure}

\subsection{The Simulations}\label{ssec:Simulations}
We perform time-domain simulations of the voltage output of the HERA feed using CST. {\bf \color{red} Rich: fill in the details here, describe the CST parameters and a brief overview of how it numerically solves for the voltages (citations?).  }

In Fig.~\ref{fig:SimulationSetup} we show the geometery of the electromagnetic simulation. A $150$\,MHz plane wave with a Gaussian envelope with FWHM of {\bf \color{red}???} is initialized {\bf \color{red} ??} meters above the dish vertex traveling in the $-z$ direction. It is reflected by the dish before entering the dipole feed, hidden below the cylindrical skirt in this figure. We record the electric field voltage of the plane wave at the feed output terminals as a function of time, plotted as a red line in Fig.~\ref{fig:SimulationOutput} along with the voltage at the feed outputs (black line). The delay between the primary envelopes of the plane wave and the voltage output of the feed is $\approx 30$\,ns which corresponds to the round trip travel time from the feed to the dish vertex and back. However, while the input plane wave, modulated by a gaussian, falls off rapidly and dies off after the first $\approx 20$\,ns after its peak, we see that the voltage output decays far more slowly with delay due to reflections within the dish-feed structure reintroducing the signal at times beyond its initial falloff. We are able to get a qualitative feel for the amplitude of the reflections by inspecting the falloff of the time domain voltage response and see that after $60$\,ns it reachs $\approx -25$\,dB.
\begin{figure}
\includegraphics[width=.5\textwidth]{figures/One_dish_Pfeed_render_pw_0deg.png}
\caption{A rendering of our time domain simulation at $t=0$, demonstrating the geometry and setup of our electromagnetic simulation. The plane wave is started just above the feed (red plane).}\label{fig:SimulationSetup}
\end{figure}
